An event-sourced and distributed database with IPLD and materialized views

### 2019-09-19 draft.tex
more
Signed-off-by: andrew <andrew@textile.io>
fix block
Signed-off-by: andrew <andrew@textile.io>

\begin{example*}
\centering
\begin{minipage}{0.7\textwidth}
\begin{lstlisting}
// Log multiaddress
 "/ipel/12D3KooWC2zyCVron7AA34N6oKNtaXaZB51feG9rBkr7QbCcW8ab"

// Encapsulated multiaddress
 "/ip4/127.0.0.1/tcp/1234/p2p/12D..dwaA6Qe/ipel/12D..bCcW8ab"

// Address book
[
  "/p2p/12D..dwaA6Qe/ipel/12D..bCcW8ab",
  "/p2p/12D..dJT6nXY/ipel/12D..bCcW8ab" // Follower
]
\end{lstlisting}
\end{minipage}
  \caption{The Log Multiaddress.}
  \label{ex:Multiaddress}
\end{example*}

@@

Example (V1, 256 bit): `bafyoiobghzefwlidfrwkqmzz2ka66zgmdmgeobw2mimktr5jivsavya`

>>>>

\begin{example*}
\centering
\begin{minipage}{0.7\textwidth}
\begin{lstlisting}[language=json,firstnumber=1]
# Log multiaddress
 /ipel/12D3KooWC2zyCVron7AA34N6oKNtaXaZB51feG9rBkr7QbCcW8ab

# Encapsulated multiaddress
 /ip4/127.0.0.1/tcp/1234/p2p/12D..dwaA6Qe/ipel/12D..bCcW8ab

# Address book
[
  /p2p/12D..dwaA6Qe/ipel/12D..bCcW8ab,
  /p2p/12D..dJT6nXY/ipel/12D..bCcW8ab # Follower
]
\end{lstlisting}
\end{minipage}
  \caption{The Log Multiaddress.}
  \label{ex:Multiaddress}
\end{example*}

@@

\begin{example}
\begin{lstlisting}
"bafyoiobghzefwlidfrwkqmzz2ka66zgmdmgeobw2mimktr5jivsavya"
\end{lstlisting}
\caption{V1, 256 bit.}
\end{example} \label{ex:v1256}
